---
title: "homework"
author: "Autumn"
date: "2/1/2017"
output: html_document
---
#Session 1 
import data
```{r}
setwd("~/Dropbox/R and Python")
library(readxl)
folderName='data'
fileName='cities.xlsx'
fileExcel=file.path(folderName,fileName)
dataFromExcel=read_excel(fileExcel,1) 
dataFromExcel
```
1.most visited in 2015
```{r}
head(dataFromExcel[order(-dataFromExcel$visits2015),],1)$city
```
or we can use
```{r}
dataFromExcel[which.max(dataFromExcel$visits2015),]$city
```
2.least visited in Aisa in 2013
first we want select Asia cities from all regions
```{r}
cityAsia=dataFromExcel[dataFromExcel$region=='Asia',]
cityAsia
```
then
```{r}
head(cityAsia[order(cityAsia$visits2013),],1)$city
```
or 
```{r}
cityAsia[which.min(cityAsia$visits2013),]$city
```
3. three least visited in Aisa in 2015
```{r}
head(cityAsia[order(cityAsia$visits2015),],3)$city
```
4. most visited in Aisa in 2013
```{r}
cityAsia[which.max(cityAsia$visits2013),]$city
```
4. and least visited in Aisa in 2013
```{r}
cityAsia[which.min(cityAsia$visits2013),]$city
```
#Session 2
1.most visited in 2015
```{r}
Most2015=0
for (visits2015 in dataFromExcel$visits2015){
  if (!is.na(visits2015)& Most2015<visits2015 ){
    Most2015=visits2015
  } 
}

dataFromExcel[!is.na(dataFromExcel$visits2015)& dataFromExcel$visits2015==Most2015,]$city
```
2.least visited in Aisa in 2013
```{r}
cityAsia=dataFromExcel[dataFromExcel$region=='Asia',]

L2013A=100
visits2013 = cityAsia$visits2013

for(visits2013 in cityAsia$visits2013){
  if (visits2013<L2013A & !is.na(visits2013)){
    L2013A=visits2013
  }
}

dataFromExcel[!is.na(dataFromExcel$visits2013)& dataFromExcel$visits2013==L2013A,]$city

```
3. three least visited in Aisa in 2015
```{r}
Least2015Asia1=100
Least2015Asia2=100
Least2015Asia3=100
posLeast2015Asia1=c()
posLeast2015Asia2=c()
posLeast2015Asia3=c()
posLeast2015Asia=c()

cityAsia=dataFromExcel[dataFromExcel$region=='Asia',]

numRows=nrow(cityAsia)
numCols=ncol(cityAsia)

for (position in 1:numRows){
  visits2015 = cityAsia[position,'visits2015']
  if(visits2015<Least2015Asia1 & !is.na(visits2015)){
    Least2015Asia1=visits2015
  }
}

for (position in 1:numRows){
  visits2015 = cityAsia[position,'visits2015']
  if(visits2015==Least2015Asia1){
    posLeast2015Asia1=c(posLeast2015Asia1,position)
  }
}

for (position in 1:numRows){
  visits2015 = cityAsia[position,'visits2015']
  if(visits2015<Least2015Asia2 & !is.na(visits2015) & visits2015>Least2015Asia1){
    Least2015Asia2=visits2015
  }
}

for (position in 1:numRows){
  visits2015 = cityAsia[position,'visits2015']
  if(visits2015==Least2015Asia2){
    posLeast2015Asia2=c(posLeast2015Asia2,position)
  }
}

for (position in 1:numRows){
  visits2015 = cityAsia[position,'visits2015']
  if(visits2015<Least2015Asia3 & !is.na(visits2015) & visits2015>Least2015Asia2){
    Least2015Asia3=visits2015
  }
}

for (position in 1:numRows){
  visits2015 = cityAsia[position,'visits2015']
  if(visits2015==Least2015Asia3){
    posLeast2015Asia3=c(posLeast2015Asia3,position)
  }
}

posLeast2015Asia=c(posLeast2015Asia1,posLeast2015Asia2,posLeast2015Asia3)
cityAsia[posLeast2015Asia,]$city
```
#Session 3
RaiseToPowerPlus 
```{r}
RiseToPowerPlus=function(base,exponent=2){
  result=1
  if (exponent > 0){
    for (time in 1:exponent){
      result=result*base
    }
  }
  if (exponent < 0){
    exponent=-exponent
    for (time in 1:exponent){
      result=result/base
    }
  }
  return(result)
}
```
testing
```{r}
RiseToPowerPlus(9,2)
RiseToPowerPlus(2,-2)
```
reduce 'for' loop 
```{r}
factors1=function(number){
  vectorOfAnswers=c() 
  for (i in 1:sqrt(number)){
    if ((number %% i) == 0){ 
      vectorOfAnswers=c(vectorOfAnswers,i,number/i)
    }
  }
  return (vectorOfAnswers) 
}
```
testing
```{r}
factors1(4)
```
avoid negative values or zeros as input
```{r}
factors2=function(number){
  vectorOfAnswers=c() 
  if (number<=0){
    return(print('0 or negative numbers are not accepted'))
    break
  }
  for (i in 1:sqrt(number)){
    if ((number %% i) == 0){ 
      vectorOfAnswers=c(vectorOfAnswers,i,number/i)
    }
  }
  return (vectorOfAnswers) 
}
```
testing
```{r}
factors2(20.9) 
factors2(0)
factors2(-20)
```
only positive integer values 
```{r}
factors3=function(number){
  vectorOfAnswers=c() 
  if (number>0 & number%%1==0){
    for (i in 1:sqrt(number)){
      if ((number %% i) == 0){ 
        vectorOfAnswers=c(vectorOfAnswers,i,number/i)
      }
    }
  return (vectorOfAnswers) 
  }else {
    print('only positive intergers are accepted')
  }
}
```
testing
```{r}
factors3(2) 
factors3(0)
factors3(3.3)
```
extra colums
```{r}
functionExtra=function(vct1,vct2){
  for (val in vct1){
    sumvct=(vct1+vct2)
    difvct=(vct1-vct2)
    mltvct=(vct1*vct2)
    divvct=(vct1/vct2)
  }
  extraDF=data.frame(number1=vct1,number2=vct2,sum=sumvct,difference=difvct,multipilication=mltvct,division=divvct)
  extraDF
}
```
testing
```{r}
functionExtra(factors3(10),factors3(4))
```
understand the function
```{r}
strangerF=function(x){
  answer=0
  change=T
  for (value in x){
    if (change){
      answer=answer+value
    }else{
      answer=answer-value
    }
    change=!change 
  }
  return (answer)
}
```

strangerF sums the first value in the list, minus second value, sums the third, minus the fourth and so on. For example, if I have (1,2,3,4,5), strangerF gives the answer of "+1-2+3-4+5"

```{r}
A=c(10,20,30,40,50)
strangerF(A)
```


```{r}
folderName='data'
fileName='dataforstrangeF.csv'
pathToFile='data/dataforstrangeF.csv'
dataF=read.csv(pathToFile)
dataF
```

StrangerF can be applied to the vals2 and vals3 columns because values in these two column are nemeric.
apply doesn't work, becaues it applys StrangerF to each column.(strangerF can't be applied to the vals1 column)
lappy donsn't work, it applys strangerF by column or by row.(strangerF can't be applied to values in the vals1 column)
mapply, Map, Filter,don't work.



